---
title: "Homework 1"
author: "Enter Name Here"
date: 'Due: May 26th @ 11:59 PM CST'
output:
  html_notebook: default
  html_document: default
---

## Learning objectives
In this homework, you will demonstrate how to change working directories, import experimental data, create summary tables, use R-packages, and use/manipulate data tables.

# Part 1: Set Up

1. Change the working directory to a local folder (folder on your computer) where you want to save your homework.
```{r}
# Insert code here

```

2. Import the data set, webstar.dta:  [http://economics.mit.edu/faculty/angrist/data1/mhe/krueger](http://economics.mit.edu/faculty/angrist/data1/mhe/krueger)
```{r}
# Insert code here

```

*Hint: .dta is Stata data format*

Names and descriptions of variabes can be found in webstarinfo.txt. 

3. Explore this study:
[https://www.aft.org/sites/default/files/periodicals/STARSummer99.pdf](https://www.aft.org/sites/default/files/periodicals/STARSummer99.pdf). Give a brief summary (1-2 paragraphs) of the experiment and why it was performed. 

- Insert discussion here

# Part 2: Creating a summary table

4. Create a nice table that shows the proportion of students who:
- are in a small class
- have a regular/aid in class
- are white or caucasian
- receive free lunch 
- have a non-white teacher
- have a teacher with a Master's degree

*Hint: you should consider using the stargazer package*  [https://cran.r-project.org/web/packages/stargazer/vignettes/stargazer.pdf](https://cran.r-project.org/web/packages/stargazer/vignettes/stargazer.pdf)

```{r }
# Insert code here

```
# Part 3: Creating a subset of the data

5. Subset the data so that only the variables discussed in webstarinfo.txt are kept. Rename this data set and save it to your local file. 

```{r}
# Insert code here

```



